\documentclass{adk_cv}
\usepackage[margin=0.4in]{geometry}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage{dashrule}
\usepackage{tikz}

\pagenumbering{}


\definecolor{default}{HTML}{4c566a}



\begin{document}

\color{default}
\noindent \titletext{Alexander Kingston}{Mathematician / Software Engineer}

\noindent adkingston@gmail.com \hfill / \hfill +1 703.618.2227 \hfill / \hfill Washington, D.C, U.S.A. \hfill / \hfill linkedin.com/in/alexanderkingston
\noindent\rule{\textwidth}{1pt}

\begingroup\hspace{-20pt}\endgroup
\begin{minipage}[t]{\dimexpr.36\linewidth}
    \begin{flushleft}
    \section{Summary}
    I am a \textit{pure mathematician} and \textit{software engineer} capable of conceptualising complex data systems quickly and efficiently.
    I am passionate about machine learning and artificial intelligence, and the impact that advanced systems can have on improving processes and peoples digital experiences.

\section{Technical Skills}
\subsection{Languages}
Go, Python (strong)

Java, Javascript (familiar)

C, Rust (learning)

\subsection{Databases}
DGraph, MongoDB, SQL, InfluxDB


\subsection{Technologies}
Docker, Kubernetes (K8S), Apache Kafka, RabbitMQ, GraphQL, REST, gRPC


\subsection{Operating Systems}
Linux (Ubuntu / Debian), Windows 10

\section{Interests}
\subsection{Technological}
Built a dedicated computer for artificial intelligence / machine learning research; implementing algorithms using Python (and occasionally experimenting with Lua or Julia) \\ 

\section{Languages}
\subsection{Fluent/Native}
English, Spanish
    \end{flushleft}
\end{minipage}
\hfill\begingroup\hspace{-15pt}\endgroup\hfill
\begin{minipage}[t]{\dimexpr.62\linewidth}

\begin{flushleft}
\section{Education}
\educationHeader{Master of Science in Data Science, Technology, \& Innovation}{University of Edinburgh, Scotland \hfill Est. 2024}

\educationHeader{Master of Science in Mathematics with Distinction}{University of St.\ Andrews, Scotland \hfill 2018}

\hspace{10pt}{\footnotesize Dissertation: \textit{Fractal Symphonies: Zeta Functions \& Tube Formulae}}

\educationHeader{Master of Arts (Hons.) in Mathematics}{University of St. Andrews, Scotland \hfill 2017}

\hspace{10pt}{\footnotesize Dissertation: \textit{On the Coordinate Functions of the Sierpi\'nski-Knopp Space Filling Curve}}

\section{Work Experience}
\educationHeader{StealthPath Inc.}{Vice President of Product Development \hfill Nov. 2021 --- Present}
Responsible for the development of the ZSuite collection of programs, which include ZAware, ZAlert, and ZProtect. Together they make up a robust intrusion detection system and automated incident response solution that focuses on behavioural analytics of network traffic, which then alerts to anomalous connections which are indicative of operational failures or malicious attacks. 
\begin{itemize}[left=0pt]
    \setlength\itemsep{-0.25em}
    \item Lead team of developers in finalisation of proof of concept program
    \item Design and architect core system to move from proof of concept to enterprise level software
    \item Present product vision and roadmap to potential investors
    \item Manage deployment at government sponsored cyber-security exercise where new requirements necessitated quick redesign of the deployment strategy resulting in the general simplification and automation of the system's installation
    \item Assist in the architecture and implementation of deployment automation for Docker Swarm and Kubernetes following cyber-security exercise  
    \item Propose novel use of DevSecOps tools for efficient ML Ops in production air-gapped environments for self-improving machine learning models
    
\end{itemize}

\educationHeader{Securiport LLC.}{Software Engineer \hfill Oct. 2018 --- Nov. 2021}
Core team member responsible for developing the \textit{Intelligent Information Management System} --- 
a proprietary system that provides border security officers with aggregated information, travel data, and 
findings on persons of interest.
\begin{itemize}[left=0pt]
\setlength\itemsep{-0.25em}
    \item Designed and managed data model for traveller and their information including documents, survey responses, travel history, and unstructured web data.
    \item Designed and implemented IDAS (Intelligent Data Analysis System), which provides a framework for the development and deployment of synchronous and asynchronous data processing and enriching pipelines with a focus of ease and flexibility of development and deployment.
    \item Created and integrated safeguards to ensure that connection and transaction failures with the databases and APIs do not disrupt the end users session.
    \item Mentored junior developers and new hires, introduced and taught our system, the tools we use, and how to develop efficiently and with production in mind.
\end{itemize}
\end{flushleft}
\end{minipage}
%\end{minipadocument}
\end{document}
